%!TEX program = pdflatex
\documentclass[letterpaper,13pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks,linkcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}[label={\small$\bullet$}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%---------- RESUME START ----------
\begin{document}

\begin{center}
    {\Huge \scshape Shenyao Jin} \\ \vspace{1pt}
    \small Department of Geophysics, Colorado School of Mines \\
    \small East Classroom Building, 901 17th St., Golden, CO 80401 \\
    \small \underline{shenyaojin@mines.edu} $|$ {+1\ (310) 256-7875} $|$ \href{https://www.linkedin.com/in/shenyao-jin/}{\underline{linkedin.com/in/shenyao-jin}} \\
\end{center}

%----------- EDUCATION -----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
  {Colorado School of Mines, Reservoir Characterization Project}{Golden, Colorado}
  {\textbf{Ph.D. Geophysics}}{Aug 2023 -- May 2027}
  \resumeItemListStart
    \resumeItem{Advisor: Dr. Ge Jin, Committee Chair: Dr. Hossein Kazemi}
    \resumeItem{\textbf{Focus}: \textit{Seismic imaging and inversion, distributed fiber-optic sensing (DFOS), velocity analysis, numerical modeling, and signal processing for subsurface characterization}}
    \resumeItem{\textbf{Minor:} \textit{Computer Science}}
  \resumeItemListEnd

\resumeSubheading
  {Zhejiang University}{Hangzhou, China}
  {\textbf{B.S. Geoscience}}{Sept 2019 -- Aug 2023}
  \resumeItemListStart
    \resumeItem{\textbf{Thesis}: ``Clustering-Based Joint Inversion for Imaging Shallow Subsurface Geological Targets''}
    \resumeItem{Thesis Advisor: Dr. Zhanjie Shi}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- SKILLS -----------
\section{Technical Skills}
\resumeItemListStart
\resumeItem{
  \textbf{Programming:} Python, MATLAB, C/C++, \LaTeX, Bash; proficient in Linux/Unix environments and Git-based workflows
}
\resumeItem{
  \textbf{Software and Packages}: Seismic Un*x, MOOSE (Multiphysics Object-Oriented Simulation Environment), DASCore (Distributed Acoustic Sensing data processing), Devito, NumPy, pandas, Matplotlib
}
\resumeItem{
  \textbf{Inverse Problems \& Optimization}: Gauss-Newton iteration, gradient-based optimization, regularization techniques, Tikhonov inversion, history matching, parameter estimation
}
\resumeItem{
  \textbf{Geophysical Methods:} Seismic data preparation and quality review, seismic interpretation, velocity analysis support, subsurface mapping, well-log integration, DFOS/DAS processing
}
\resumeItem{
  \textbf{Imaging Workflow \& Reporting}: Testing and evaluating imaging workflows, cross-section and map preparation, technical reporting, presentation development, and detail-oriented QC
}
\resumeItem{
  \textbf{Data Science Practices:} Data cleaning and quality control, reproducible analysis pipelines, scientific visualization, and exploratory ML-based quality diagnostics
}
\resumeItem{
  \textbf{Related Coursework:} Inversion Theory, Advanced Machine Learning, Reservoir Simulation, Advanced Geophysical Computing, Advanced Data Science, Numerical Methods, Statistics
}
\resumeItem{
  \textbf{Productivity Tools:} Microsoft Word, Excel, and PowerPoint
}
\resumeItem{\textbf{Software Development:} Author of \href{https://github.com/shenyaojin/fibeRIS}{fibeRIS}, an open-source Python package for history matching and interpretation of DAS data (github.com/shenyaojin/fibeRIS).}
\resumeItemListEnd

%----------- Experience  -----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
  {Graduate Research Assistant}{Golden, Colorado}
  {Reservoir Characterization Project, Colorado School of Mines}{Aug 2023 -- Present}
  \resumeItemListStart
    \resumeItem{\textbf{Cement Quality Monitoring using Low-Frequency DAS (ExxonMobil Project Mariner)}}
      \resumeItemListStart
        \resumeItem{Built an end-to-end LF-DAS workflow (data preparation, quality control, and analysis) and field deployment strategy to evaluate cement quality in horizontal wells.}
        \resumeItem{Implemented a coupled pressure-strain numerical model in MOOSE to support velocity-sensitive response analysis and imaging-oriented interpretation under different cementing conditions.}
        \resumeItem{Integrated LF-DAS responses with well information, documented findings, and delivered concise progress updates in weekly sponsor meetings.}
      \resumeItemListEnd

    \resumeItem{\textbf{Permeability Inversion from DAS Data (ExxonMobil Collaboration)}}
      \resumeItemListStart
        \resumeItem{Formulated and solved an inverse problem for low-frequency DAS data to quantify in-situ permeability using physics-based forward modeling and optimization algorithms.}
        \resumeItem{Evaluated workflow outputs across field scenarios through iterative history matching and comparative testing with team guidance.}
        \resumeItem{Validated interpretations against well logs and operational constraints, and prepared technical materials for review meetings and project presentations.}
      \resumeItemListEnd

    \resumeItem{\textbf{Geothermal Energy Systems Data Interpretation (Fervo Energy Collaboration)}}
      \resumeItemListStart
        \resumeItem{Collaborating with Rice University and Fervo Energy to interpret multi-source geophysical datasets (DAS, sonic, and seismic) for subsurface evaluation.}
        \resumeItem{Preparing figures, maps, and presentation-ready technical notes to communicate imaging observations and recommendations in cross-functional team settings.}
      \resumeItemListEnd
  \resumeItemListEnd

\resumeSubheading
  {Graduate Research Intern}{Idaho Springs, Colorado}
  {Reservoir Characterization Project, Colorado School of Mines}{May 2025 -- Aug 2025}
  \resumeItemListStart
    \resumeItem{Conducted DOE-funded research on monitoring induced fracture propagation using low-frequency DAS; developed novel data acquisition and processing strategies.}
    \resumeItem{Designed and deployed a novel U-shaped fiber-optic cable in monitoring wells with co-located DTS and DSS sensing fibers, advancing field deployment methodologies.}
    \resumeItem{Analyzed multi-channel DAS datasets to extract fracture signatures, support imaging workflow validation, and document outcomes while following field safety procedures and reporting requirements.}
  \resumeItemListEnd

\resumeSubheading
  {Undergraduate Research Intern}{Golden, Colorado}
  {Reservoir Characterization Project, Colorado School of Mines}{July 2022 -- September 2022}
  \resumeItemListStart
    \resumeItem{Developed data processing workflows for low-frequency DAS data collected in Lake Hattie, Wyoming; implemented velocity scanning for improved imaging quality review.}
    \resumeItem{Contributed to DAS-based subsurface imaging workflow development and applied signal processing techniques to improve data quality and interpretation consistency.}
  \resumeItemListEnd

\resumeSubheading
  {Undergraduate Research Assistant}{Hangzhou, China}
  {School of Geosciences, Zhejiang University}{Sept 2021 -- June 2023}
  \resumeItemListStart
    \resumeItem{Developed advanced joint inversion algorithms in \textit{C++} to solve coupled seismic and electromagnetic inverse problems for subsurface characterization.}
    \resumeItem{Implemented optimization techniques including Gauss-Newton iteration and regularization methods to improve inversion stability and convergence.}
    \resumeItem{Validated inversion algorithms on field datasets and well log data, demonstrating practical effectiveness in resolving subsurface geological structures.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- Abstracts and Presentations -----------
\section{Abstracts and Presentations}
\resumeSubHeadingListStart
  \resumeItem{\textbf{Shenyao J.}, Ge J. \textit{Low-Frequency DAS for Cement Quality Monitoring in Horizontal Wells}}
  \resumeItemListStart
    \resumeItem{URTeC 2026, Houston, Texas. Oral Presentation (Abstract Accepted).}
    \resumeItem{SEG-AAPG IMAGE 2025, Houston, Texas. Oral Presentation.}
    \resumeItem{American Geophysical Union Fall Meeting 2025, New Orleans, Louisiana. Oral Presentation.}
    \resumeItem{RCP Sponsor Meeting 2025, Golden, Colorado. Oral Presentation.}
  \resumeItemListEnd
  \resumeItem{\textbf{Shenyao J.}, Ge J. \textit{Conductive Fracture Monitoring Using Distributed Strain Sensing: From Stimulation to Production}}
  \resumeItemListStart
    \resumeItem{SEG-AAPG IMAGE 2024, Houston, Texas. Poster Presentation.}
    \resumeItem{RCP Sponsor Meeting 2024, Golden, Colorado. Oral Presentation.}
  \resumeItemListEnd
\resumeSubHeadingListEnd



%----------- PUBLICATIONS -----------
\section{Publications}
\resumeSubHeadingListStart
    \resumeItem{\textbf{Jin, S.}, and Jin, G. (2026). Low-Frequency DAS for Cement Quality Monitoring in Horizontal Wells: Seismic Inversion and Optimization Perspectives. \textit{SPE Journal} (in review); abstract submitted to URTeC 2026.}
    \resumeItem{Mao, F., Yang, B., \& \textbf{Jin, S.} (2025). Recovering missing regions of earth magnetic anomaly grid data (EMAG2) using RePaint based on diffusion model. \textit{Big Data and Earth System}, 1(1), 100004.}
\resumeSubHeadingListEnd


%----------- HONORS AND AWARDS -----------
\section{Honors and Awards}
\resumeSubHeadingListStart

\resumeProjectHeading
  {\textbf{George R. Pickett Memorial Scholarship}}{Oct 2024}
\resumeItemListStart
  \resumeItem{Awarded for excellence in borehole geophysics with applied focus on oil and gas workflows.}
\resumeItemListEnd

\resumeProjectHeading
  {\textbf{First-Year Fellowship for Graduate Students}}{Mar 2024}
\resumeItemListStart
  \resumeItem{Awarded by the Colorado School of Mines to recognize incoming students for integrating computational geophysics to advance sustainable energy systems.}
\resumeItemListEnd

\resumeProjectHeading
  {\textbf{Meritorious Winner, Mathematical Contest in Modeling (MCM)}}{Feb 2022}
\resumeItemListStart
  \resumeItem{Top 8\% of international undergraduate teams. Contributed as lead programmer and data analyst.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
